Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2016-10-31 ms_pre_post.Rmd
Edit second paragraph of Introduction

@@

Severe inbreeding depression might cause selection for alleles underlying active pre- and post-copulatory inbreeding avoidance and associated polyandry, but if evolution of one strategy renders its complement redundant for avoiding inbreeding, then selection might instead be sustained over generations for only one strategy. Empirical studies of multiple species have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013; @Fischer2015], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009]. Further, evidence of both pre-copulatory and post-copulatory inbreeding avoidance has been found for a handful of well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015], while @Liu2014 found evidence for pre-copulatory, but not post-copulatory, inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*). Other studies do not find any evidence for inbreeding avoidance despite strong inbreeding depression, suggesting that evolution of pre- or post-copulatory inbreeding avoidance cannot be presumed [e.g., @Frere2010; @Reid2014; @Reid2015]. These empirical studies demonstrate that all combinations of adaptive pre-copulatory and post-copulatory inbreeding avoidance are possible, but no conceptual framework exists to predict *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry, can evolve.

>>>>

Meanwhile, empirical studies of diverse species have found evidence for female inbreeding avoidance enacted through pre-copulatory or post-copulatory routes, or both. For example, pre-copulatory inbreeding avoidance has been documented in weevils, birds, and butterflies [e.g., @Kuriwada2011; @Kingma2013; @Fischer2015], and post-copulatory inbreeding avoidance has been documented in crickets [e.g., @Simmons2006; @Bretman2009]. Evidence of both pre-copulatory and post-copulatory inbreeding avoidance has accumulated for some well-studied species, including Trinidadian guppies [*Poecilia reticulata*; @Gasparini2011; @Daniel2015] and house mice [*Mus domesticus*; @Potts1991; @Firman2015]. While most studies consider either pre- or post-copulatory inbreeding avoidance in isolation, a small number of studies consider both. Accordingly, @Liu2014 found evidence of pre-copulatory, but not post-copulatory, inbreeding avoidance in cabbage beetles (*Colaphellus bowringi*). Other studies found no evidence of pre- or post-copulatory inbreeding avoidane despite strong inbreeding depression [e.g., @Reid2014; @Reid2015]. These empirical studies demonstrate that diverse combinations of pre- and post-copulatory inbreeding avoidance occur in nature. However, there is as yet no conceptual framework that predicts *a priori* what combinations should be favoured by selection when both pre- and post-copulatory inbreeding avoidance, and polyandry can evolve. Such a framework would allow prediction of the form of mating system evolution across different systems that experience inbreeding depression and allow existing empirical studies to be used to test evolutionary predictions through comparative analyses.

<!--- The terminal sentence is non-sensical. It confuses what theory actually is and suggests a post-hoc testing of a model through already existing data -- what does *prediction* even mean in this context !? This is bad science. --->

@@
